%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (Modified for Aayush Rajput)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-11pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-11pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Aayush Rajput} \\ \vspace{3pt}
    \small 6398794538 $|$ \href{mailto:aayushpratapsingh001@gmail.com}{\underline{aayushpratapsingh001@gmail.com}} $|$ 
    \href{https://linkedin.com/in/aayush-rajput-38142827b}{\underline{linkedin.com/in/aayush-rajput}} $|$
    \href{https://github.com/aayushrajputz}{\underline{github.com/aayushrajputz}} \\ \vspace{2pt}
    \small \href{https://leetcode.com/aayush_rajput/}{\underline{leetcode.com/aayush\_rajput}} $|$
    \href{https://codolio.com/profile/Aayushrajput}{\underline{codolio.com/profile/Aayushrajput}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
 \small{Dedicated \textbf{Software Engineer} and \textbf{Product Founder} with 1+ years of experience in building high-performance web services. Successfully scaled a global SaaS platform (\textbf{BinaryPDF}) from 0 to launch, handling multi-national traffic from \textbf{5+ countries} while sustaining \textbf{1,000+ concurrent requests} with sub-100ms latency. Leveraged advanced data structures and algorithm design to optimize real-world backend infrastructure and cloud storage spend by 60\%.}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BinaryPDF (SaaS Platform)}{Jan. 2025 -- Present}
      {Founder \& Lead Backend Engineer}{Noida, India}
      \resumeItemListStart
        \resumeItem{Architected a high-concurrency \textbf{Golang} backend that sustained \textbf{1,000+ concurrent requests} with sub-100ms latency, validated through k6 load-testing for production-grade robustness.}
        \resumeItem{Spearheaded a **Global Product Launch** on Product Hunt and Dev.to, achieving \textbf{140+ unique visitors within 24 hours} and managing traffic across \textbf{5+ countries} (USA, Nigeria, Philippines, Georgia, India).}
        \resumeItem{Engineered a custom object storage integration with \textbf{Cloudflare R2}, slashing infrastructure spend by \textbf{60\%} and lower file-retrieval latency by \textbf{45\%} through edge-caching and service-layer optimization.}
        \resumeItem{Built and integrated \textbf{Firebase Auth} and \textbf{Razorpay REST APIs} within an object-oriented service architecture, ensuring \textbf{99.9\% reliability} for multi-tenant access and secure payment flows.}
        \resumeItem{Leveraged Go \textbf{Concurrency Patterns} (Goroutines, Channels, Semaphores) to parallelize OCR and PDF merging, boosting system throughput by \textbf{3x} and scaling the professional network to \textbf{1,200+ followers}.}
        \resumeItem{Orchestrated modular backend services using \textbf{Docker} containerization, automating CI/CD pipelines that trimmed weekly deployment cycles by \textbf{12 hours}.}
      \resumeItemListEnd

    \resumeSubheading
      {Technical Contributor (takeuforward.org)}{Feb. 2026}
      {QA \& Systems Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Identified a critical session-handling inconsistency affecting eventually consistency on the TUF platform, leading to an \textbf{architectural fix} that restored reliable data sync for \textbf{5,000+ active students}.}
        \resumeItem{Analyzed real-time progress-tracking mechanisms and \textbf{Session TTL} mismatches using systematic data analysis, designing algorithmic corrections to ensure 100\% student progress accuracy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Distributed AI Orchestration Engine} $|$ \emph{Node.js, GraphQL, Reverse Engineering}}{Jan. 2026}
          \resumeItemListStart
            \resumeItem{Reverse-engineered complex \textbf{GraphQL APIs} to automate enterprise promotion logic, eliminating manual intervention and ensuring \textbf{100\% execution accuracy}.}
            \resumeItem{Designed a custom entity discovery engine to autonomously resolve environment-specific \textbf{UUIDs}, leading to a \textbf{90\% reduction} in system integration time.}
          \end{itemize}
      \resumeProjectHeading
          {\textbf{AI-Powered Financial Tracker} $|$ \emph{Golang, Gin, OpenAI, Docker}}{Oct. 2024}
          \resumeItemListStart
            \resumeItem{Developed an automated classification pipeline using \textbf{OpenAI's API}, achieving \textbf{95\% accuracy} in parsing fiscal data and reducing manual entry time by \textbf{50\%}.}
            \resumeItem{Optimized backend performance and maintainability by applying advanced data structures and algorithms, ensuring sub-50ms response times for data processing.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go (Golang), Java, JavaScript, TypeScript, SQL, C++, HTML/CSS} \\
     \textbf{Backend/Tools}{: Node.js, Gin, Express.js, REST APIs, GraphQL, Redis, Docker, Git} \\
     \textbf{Infrastructure}{: Cloudflare R2, Firebase, PostgreSQL, MongoDB, Object Storage} \\
     \textbf{Problem Solving}{: \textbf{Advanced Proficiency in Data Structures and Algorithms}, with a focus on Graphs, Trees, and Dynamic Programming; applied these patterns to optimize real-world backend performance, concurrency, and distributed system reliability.}
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Swami Vivekanand Subharti University}{Meerut, UP}
      {Bachelor of Technology in Computer Science $|$ \textbf{CGPA: 8.4}}{2021 -- 2025}
  \resumeSubHeadingListEnd


%-----------CERTIFICATIONS-----------
\section{Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Backend Development (Golang)} - GeeksforGeeks (2025) \\
     \textbf{Problem Solving (Basic)} - HackerRank (2025)
    }}
 \end{itemize}

\end{document}
